Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-11 paper/structureScene.tex
punctuation and spelling in conclusion

Abstracting the scene as a reduced set of exemplars with adapted similarity strategies allows us to improve ASSR performance when the BOF approaches based on GMMs fails with reference to an early integration scheme. Those results advocate for a hierarchical model of the scene, where small time scale structure  (below a second) shall be decorelated using convolutional network such as the ones of the scattering transforms and larger time scale (over a second) structure shall be modeled as adaptive aggregates that can be identified in the time domain in an unsupervised setting and in the features domain in the supervised case (provided that the dimensionality is sufficiently high).

>>>>

Abstracting the scene as a reduced set of exemplars with adapted similarity strategies allows us to improve ASSR performance when the BOF approaches based on GMMs fails with reference to an early integration scheme. Those results advocate for a hierarchical model of the scene, where small time scale structure -- \ie below a second -- shall be decorrelated using ca onvolutional network such as in the scattering transform, whereas larger time scales -- \ie over a second -- structure shall be modeled as adaptive aggregates that can be identified in the time domain in an unsupervised setting and in the features domain in the supervised case, provided that the dimensionality is sufficiently high.
